Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-07-21 Master Thesis/synopsis.tex
Complete proof of 2.2

The second assertion follows from the first and from \cite{Ka79}, §5, Theorem 1.
\end{proof}

>>>>

For the second assertion, let $K$ be not algebraically closed and $v=v(w_1)=v(w_2)\in\operatorname{Spv}_\text{d}^{(1)}(K)$. The restriction $v|$ of $v$ on $k=\mathbb{Q}(T)\subset K$ is a discrete valuation. Choose a henselization $k_{v|}$ of $k$ such that $k_{v|}\subset K$ and consider the absolute inertia field $k_{v|}^\text{t}$ of $k_{v|}$. Since $k(v)$ is separably closed, we have $k_{v|}^\text{t}\subset K$. Since $v|\in \operatorname{Spv} ({k_{v|}^\text{t}})$ is discrete and henselian, \cite{Ka79} §5, Theorem 1 shows $\operatorname{cd}(k_{v|}^\text{t})\leq 2$. In particular, $\operatorname{cd}(K)\leq 2$.
\end{proof}
